Community-Conditioned Language Models

### 2020-11-20 paper/paper.tex
more todos done

However, we observe that community-wise CCLM perplexity is only weakly (if at all) \bn{Changed the indiscernability (y-axis) from entropy to Ppl and the p-values all shot up above 0.1. However the r is still very weakly positive for every model.}\jp{Are indiscernability values correct? Seems inconsistent with the confusion matrix.}
correlated with community indiscernibility under the corresponding latent 
LMCC (see \cref{fig:cclm_lmcc_ppl} and \cref{tab:cclm_lmcc_ppl}).
In other words, the linguistic complexity of a given community
is a poor predictor of how distinct its language is.

\jp{actually, if we had many more communities, then the lines could be ``more blurred'' between various communities, and we may have a stronger correlation here.}
\begin{figure}
  \pplscatter{lstm-3-1_cclm}{lstm-3-1_lmcc}
  \caption{%
    Mean community-wise linguistic perplexity (x-axis) 
    and indiscernibility (y-axis) 
    (Pearson's r = \num{0.16}; p = \num{0.2991}).  
    Shown here for the LSTM with $c = 1$.}
  \label{fig:cclm_lmcc_ppl}
\end{figure}

@@

We cannot exclude a correlation (\cref{tab:cclm_lmcc_ppl}) between the perplexity of the
% \bn{I'm not sure if we can make this claim or not with the Ppl-Ppl correlations. However, given that *all* of them have positive correlation, even though the p-values are somewhat higher than .1 maybe we can?}
CCLM and the indiscernibility of the corresponding community
\ref{hyp:rich-harder-to-identify}. Because we have relatively few,
and only large communities in our test set, it is difficult to
provide a conclusive answer, but this kind of correlation would suggest that
community-specific complexity can be partially attributed to using
more varied patterns. However, even the most complex communities
(perplexity per word above 100) have an indiscernibility of about 3
(out of a maximum of 46)\jp{make consistent with data}, so they retain fairly specific patterns:
they are not simply an even mixture of the kind of comments found in
other communities.

>>>>

However, we observe that community-wise CCLM perplexity is only weakly (if at all) \bn{Changed the indiscernability (y-axis) from entropy to Ppl and the p-values all shot up above 0.1. However the r is still very weakly positive for every model.}
correlated with community indiscernibility under the corresponding latent 
LMCC (see \cref{fig:cclm_lmcc_ppl} and \cref{tab:cclm_lmcc_ppl}).
In other words, the linguistic complexity of a given community
is a poor predictor of how distinct its language is.

\begin{figure}
  \pplscatter{lstm-3-1_cclm}{lstm-3-1_lmcc}
  \caption{%
    Mean community-wise linguistic perplexity (x-axis) 
    and indiscernibility (y-axis) 
    (Pearson's r = \num{0.16}; p = \num{0.2991}).  
    Shown here for the LSTM with $c = 1$.}
  \label{fig:cclm_lmcc_ppl}
\end{figure}

@@

We cannot exclude a correlation (\cref{tab:cclm_lmcc_ppl}) between the perplexity of the
% \bn{I'm not sure if we can make this claim or not with the Ppl-Ppl correlations. However, given that *all* of them have positive correlation, even though the p-values are somewhat higher than .1 maybe we can?}
CCLM and the indiscernibility of the corresponding community
\ref{hyp:rich-harder-to-identify}. Because we have relatively few,
and only large communities in our test set, it is difficult to
provide a conclusive answer, but this kind of correlation would suggest that
community-specific complexity can be partially attributed to using
more varied patterns. However, even the most complex communities
(perplexity per word above 100) have an indiscernibility of about 3
(out of a maximum of 46)\jp{make consistent with data once the plot is stablilized}, so they retain fairly specific patterns:
they are not simply an even mixture of the kind of comments found in
other communities.
